\smallskip
\noindent
\textbf{RQ4 (Ablation of Control Flow Guidance):}

\begin{table}[h]
\centering
\caption{
    \centering
    Comparison of goal violations found by \spoilsport{} with (``\spoilsport{}'') and without (``Ablated'') control flow guidance on rug-pull contracts (n=1,324). The better results are bolded.
}
\label{ss:table:rq4}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& & \multicolumn{2}{c|}{\textbf{\spoilsport{}}} & \multicolumn{2}{c|}{\textbf{Ablated}} \\
\cline{3-6}
\textbf{Role} & \textbf{Goal} & \textbf{\# Viol.} & \textbf{Time} & \textbf{\# Viol.} & \textbf{Time} \\
\hline
\multirow{3}{*}{\holder}
    & \maxowned  & \textbf{402}   & \textbf{3h 4m}   & 398   & 6h 7m \\
\cline{2-6}
    & \minsupply & \textbf{982}   & \textbf{40s}     & \textbf{982}   & 1m 19s \\
\cline{2-6}
    & \liquidity & \textbf{1,283} & \textbf{4h 19m}  & 692   & 7h 50m \\
\hline
\owner & \maxsupply & 64    & \textbf{44m}     & \textbf{76}    & 1h 19m \\
\hline
\multicolumn{2}{|l|}{\textbf{TOTAL}} & \textbf{2,731} & \textbf{8h 7m} & \textbf{2,148} & \textbf{15h 17m} \\
\hline
\end{tabular}
\end{table}

Results of the ablation are found in \autoref{ss:table:rq4}.
Overall, the ablated version took 7h 10m (88.3\%) longer to find 583 (21.3\%) fewer violations.
This difference in found violations is most pronounced in the \liquidity goal, which found 691 (50.0\%) fewer violations.
This is attributed to the \revs{fuzzer} timing out more as it needs to explore more candidates before finding the violations.
Where the \spoilsport \textit{Goal Violtion Search} hit the time limit while searching for \liquidity violations 161 times, the ablation hit the time limit 742 times.
For \maxowned and \minsupply{}, roughly the same number of violations were found but over a longer time frame.
Notably, \maxowned took almost twice as long.

Of interest, there were more \maxsupply goal violations found by the ablation.
The majority (10) of these were discovered in the \textit{MultiToken} contract (\texttt{0xb052{\allowbreak}f8a3{\allowbreak}3d8b{\allowbreak}b068{\allowbreak}414e{\allowbreak}ade0{\allowbreak}6af6{\allowbreak}9551{\allowbreak}99f9{\allowbreak}f010}) as integer overflow bugs.
While this contract guards against integer overflow with the \texttt{SafeMath} library, it fails to use this guard for a \texttt{mintTokens()} minting function.
The initial \spoilsport run does not initially chance upon function arguments that would cause this overflow and only finds a single function candidate to prepend the sequence.
Thus it has less chances to find arguments which cause \texttt{totalSupply} to overflow.
However, the ablation's search is not restricted to control flow dependencies and hence prepends additional functions, increasing the chance of hitting the integer overflow.


\begin{results}
    Without guidance from control flow dependencies, we found 538 (21.3\%) fewer violations while taking 7h 10m (88.3\%) longer.
\end{results}